Cleaning and Processing

### 2024-11-22 code/eda-code/eda-v1.qmd
Final Changes for RR
Created DiB; updates for all changes

For first pregnancy/birth, I combine all "primi" statuses and "nulli" statuses (gravida or parous) into `nulliparous`. For second or more pregnancies/births, I combine all multiple statuses (gravida or parous) into `multiparous`. This combines "multigesta", "secundigesta", and "trigesta" (-gesta in Portuguese meaning -gravida in English) into `multiparous`, since they mean the same thing (two or more pregnancies). I also combine "secundipara" and "multipara" into the category `multiparous`, since this means two or more births. The words in Portuguese and English here are the same.

@@

Using these new dummy variables, I created new dummy variables defining if the infants were normal birth weight (NBW $>2500$ g) or low birth weight (LBW $\leq2500$ g) for all infants and then stratified by maternal skin color. These are `Afro_NBW` and `Afro_LBW`; and `Euro_NBW` and `Euro_LBW`. I will use these to see how many infants were low birth weight or normal birth weight for each maternal skin category in the `introanalysis-v1.qmd` file.

@@

# Save table for supplemental analysis
saveRDS(table_nationality_stats, file = here::here("results", "tables", "table_nationality_stats_final.rds"))
```
The t-tests demonstrate no significant difference in the mean birthweight between Portuguese and all other European immigrants and between Portuguese and White Brazilian women. This suggests that differentiating European nationality further will not influence the regression results.

@@

# Display the table using flextable
table2 <- flextable(Mean_Birthweights) %>%
  set_caption("Mean Birth Weight Comparison") %>%
  align(j = 2, align = "left", part = "all") %>%
  align(j = 4, align = "right", part = "all") %>%
  set_header_labels(
    Sample = "Sample",
    Year = "Year", 
    Mean = "Mean (grams)",
    Source = "Source"
  ) %>%
  bold(part = "header") %>%
  #autofit() %>%
  set_table_properties(layout = "autofit", width = 1, align = "center")
table2

>>>>

For first pregnancy/birth, I combine all "primi" statuses and "nulli" statuses (gravida or parous) into `nulliparous`. For second or more pregnancies/births, I combine all multiple statuses (gravida or parous) into `multiparous`. This combines "multigesta", "secundigesta", and "trigesta" (-gesta in Portuguese meaning -gravida in English) into `multiparous`, since they mean the same thing (two or more pregnancies). I also combine "secundipara" and "multipara" into the category `multiparous`, since this means two or more births. The words in Portuguese and English here are the same. Gravidity refers to the total number of pregnancies a woman has, regardless of duration. Parity refers to a woman’s number of past pregnancies that reached viability and have been delivered, regardless of the number of children [@posner2013].

@@

Using these dummy variables, I created further dummy variables defining if the infants were normal birth weight (NBW $>2500$ g) or low birth weight (LBW $\leq2500$ g) for all infants and then stratified by maternal skin color. These are `Afro_NBW` and `Afro_LBW`; and `Euro_NBW` and `Euro_LBW`. I will use these to see how many infants were low birth weight or normal birth weight for each maternal skin category in the `introanalysis-v1.qmd` file.

@@

# Save table for supplemental analysis
saveRDS(table_nationality_stats, file = here::here("results", "tables", "table_nationality_stats_final.rds"))
```
The t-tests demonstrate no significant difference in the mean birth weight between Portuguese and all other European immigrants and between Portuguese and White Brazilian women. This suggests that differentiating European nationality further will not influence the regression results.

@@

# Display the table using flextable
table2 <- flextable(Mean_Birthweights) %>%
  set_caption("Mean Birth Weight Comparison") %>%
  align(j = 2, align = "left", part = "all") %>%
  align(j = 4, align = "right", part = "all") %>%
  set_header_labels(
    Sample = "Sample",
    Year = "Year", 
    Mean = "Mean (grams)",
    Source = "Source"
  ) %>%
  bold(part = "header") %>%
  #autofit() %>%
  set_table_properties(layout = "autofit", width = 1, align = "center") %>%
  add_footer_lines("*All values are sample means except the Steckel estimate, which is a regression coefficient.")
table2

### 2024-11-22 code/processing-code/processingfile-v1.qmd
Final Changes for RR
Created DiB; updates for all changes

I created this dataset from published clinical notes from a specific maternity hospital in Rio de Janeiro, Brazil for multiple projects, mostly of a qualitative nature. Thus, I was interested in the notes clinicians included on difficult deliveries and their outcomes. These variables include qualitative information that can be excluded from our processed data, since we are not looking at qualitative notes on cases. Thus, I will remove the following variables as I process the data: `Nationality_Notes`, `Maternal_Notes`, `CauseofDeath`, `PreviousHistory`, and `Notes`. Nonetheless, for `Fetal_Notes`, we need to keep the Fetal_Notes variable at the moment as it qualifies the `FetalOutcome` variable. Further, I will exclude `Birth_Notes`, but first I will need to extract information on gestation (twin versus singleton birth).

I also don't need the citation information to run regressions. So I will remove the following variables as I process our data: `VolN`, `Page`, `Number`.

@@

# Remove median and maternal age variables given missing data
Mean_Birthweights <- Mean_Birthweights %>% dplyr::select(-Median, -`Maternal Age (mean)`, -"<2500gm (%)", -`Page #`)

>>>>

I created this dataset from published clinical notes from a specific maternity hospital in Rio de Janeiro, Brazil for multiple projects, mostly of a qualitative nature. Thus, I was interested in the notes clinicians included on difficult deliveries and their outcomes. These variables include qualitative information that can be excluded from our processed data, since we are not looking at qualitative notes on cases. Thus, I will remove the following variables as I process the data: `Nationality_Notes`, `Maternal_Notes`, `CauseofDeath`, `PreviousHistory`, and `Notes`. Nonetheless, for `Fetal_Notes`, we need to keep the Fetal_Notes variable as it qualifies the `FetalOutcome` variable. Further, I will exclude `Birth_Notes`, but first I will need to extract information on gestation (twin versus singleton birth).

I also don't need the citation information to run regressions. I will remove the following variables as I process our data: `VolN`, `Page`, `Number`.

@@

# Remove median,maternal age, low brith weight, page numbers, and types of measurement variables given missing data
Mean_Birthweights <- Mean_Birthweights %>% dplyr::select(-Median, -`Maternal Age (mean)`, -"<2500gm (%)", -`Page #`, -"Measurement")
